Hrvatska u kontekstu europskih konvergencijskih klubova

### 2024-08-27 Paper.Rmd
los

```{r ljbx,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
# Function to compute Ljung-Box test p-values for every second lag
compute_ljung_box_every_second_lag <- function(data, max_lag = 20) {
  results <- list()
  for (lag in seq(2, max_lag, by = 2)) {  # Loop through every second lag
    p_value <- Box.test(data$diff_log_gdp_per_capita, lag = lag, type = "Ljung-Box")$statistic
    results[[lag]] <- tibble(lag = lag, p_value = p_value)
  }
  bind_rows(results) %>% mutate(group = data$group[1])
}

# Apply the function to the data
ljung_box_results_second_lags <- data %>%
  group_by(group) %>%
  do(compute_ljung_box_every_second_lag(., max_lag = 20)) %>%
  ungroup()

@@

# Display the results as a table
print(ljung_box_table_second_lags)
```

@@

```{r acf, libs,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
# Plot ACF values as bar charts with facets
acf_facet_plot <- ggplot(acf_results, aes(x = lag, y = acf)) +
  geom_bar(stat = "identity", fill = "black", color = "white") +
  labs(title = "ACF dijagram", x = "Lag", y = "ACF") +
  theme_minimal() +
  facet_wrap(~group, scales = "free_y")

@@

```{r frac, libs,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}

>>>>

```{r ljbx,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
compute_ljung_box_every_second_lag <- function(data, max_lag = 20) {
  results <- list()
  for (lag in seq(2, max_lag, by = 2)) {  # Loop through every second lag
    p_value <- Box.test(data$diff_log_gdp_per_capita, lag = lag, type = "Ljung-Box")$p.value
    results[[lag]] <- tibble(lag = lag, p_value = p_value)
  }
  bind_rows(results) %>% mutate(group = data$group[1])
}

# Apply the function to the data
ljung_box_results_second_lags <- diff_croatia_vs_groups %>%
  group_by(group) %>%
  do(compute_ljung_box_every_second_lag(., max_lag = 20)) %>%
  ungroup()

@@

# Display the results as a table
print(ljung_box_table_second_lags)

# Create a nice table visualization using gt
ljung_box_gt_second_lags <- ljung_box_table_second_lags %>%
  gt() %>%
  tab_header(
    title = "Ljung-Box Test P-values for Every Second Lag",
    subtitle = "P-values for every second lag up to 20 for each group"
  ) %>%
  cols_label(
    group = "Group",
    lag_2 = "Lag 2", lag_4 = "Lag 4", lag_6 = "Lag 6", lag_8 = "Lag 8", lag_10 = "Lag 10",
    lag_12 = "Lag 12", lag_14 = "Lag 14", lag_16 = "Lag 16", lag_18 = "Lag 18", lag_20 = "Lag 20"
  ) %>%
  fmt_number(
    columns = starts_with("lag_"),
    decimals = 3
  ) %>%
  tab_options(
    table.font.size = 12,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    column_labels.font.size = 12
  )

# Print the gt table
#print(ljung_box_gt_second_lags)
```

@@

```{r acf,  echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}

compute_acf <- function(data, max_lag = 20) {
  # Remove NA values before computing ACF
  data <- data %>% filter(!is.na(diff_log_gdp_per_capita))

  acf_values <- acf(data$diff_log_gdp_per_capita, plot = FALSE, lag.max = max_lag)
  tibble(lag = acf_values$lag, acf = acf_values$acf)
}

# Apply the function to your data
acf_results <- diff_croatia_vs_groups %>%
  group_by(group) %>%
  do(compute_acf(.)) %>%
  ungroup()

# Unnest the ACF values to create a flat data frame
acf_results <- acf_results %>%
  unnest(cols = c(lag, acf))

# Plot ACF values as bar charts with facets
acf_facet_plot <- ggplot(acf_results, aes(x = lag, y = acf)) +
  geom_bar(stat = "identity", fill = "black", color = "white") +
  labs(title = "ACF dijagram", x = "Lag", y = "ACF") +
  theme_minimal() +
  facet_wrap(~group, scales = "free_y")

@@

```{r frac, eval=FALSE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=6}
